Comparing the perfomance impacts of narrow and extended feature spaces for machine learning bots in the game of Schnapsen

### 2018-02-01 Text/paper.tex
This is actually the final version of the paper.tex as handed in

\clearpage
\section{Research Question}
In our research, we want to find \textit{if extending the feature set will improve the machine learning bot's performance in the game of Schnapsen}. With improve the most, we mean as seen from the baseline. There is already a machine learning bot present, which will act as this base line. This bot has, what we will call the \textit{default feature space}- provided by the framework.  \\

>>>>

\clearpage
\section{Research Question}
In our research, we want to find \textit{if extending the feature set will improve the machine learning bot's performance the most in the game of Schnapsen}. With improve the most, we mean as seen from the baseline. There is already a machine learning bot present, which will act as this base line. This bot has, what we will call the \textit{default feature space}- provided by the framework.  \\
